A performance assessment of evolutionary algorithms in volunteer computing environments

### 2016-11-13 EvoPar2017/paper.Rnw
Checking internet connection

NodIO needs a fitness function to work with; in this case the classical Trap 
function \cite{Ackley1987} has been used. % I don't think this use of the ; is correct
% Changed to .
The evolutionary algorithm that evaluates that function runs in the
browser, but the server needs to know when the solution has been
found, so a function that checks termination condition is also included in the server, as a configuration
option. In all cases we are using 50 Traps, a problem
that is difficult enough to need the intervention of several users for
an extended amount of minutes.
For every new individual sent by the clients to the cache, several
pieces of metadata were stored: a time stamp, the client IP, the chromosome and
fitness value, the cache size in that particular moment, and also if that
individual actually updated the cache or not.

>>>>

NodIO needs a fitness function to work with; in this case the classical Trap 
function \cite{Ackley1987} has been used. 
The evolutionary algorithm that uses Trap as fitness function is
completely run in the
browser, but the server needs to know when the solution has been
found, so a subroutine that checks if the solution been found  is also included in the server, as a configuration
option. In all cases we are using 50 Traps, a problem
that is difficult enough to need the intervention of several users for
an extended amount of minutes.
For every new individual sent by the clients to the cache, several
pieces of metadata were stored: a time stamp, the client IP, the chromosome and
fitness value, the cache size in that particular moment, and also if that
individual actually updated the cache or not.
